\documentclass[a4paper,10pt]{article}

% Packages
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\pagestyle{empty}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=black
}

% Section styling
\usepackage{titlesec}
\titleformat{\section}
  {\bfseries\uppercase}{}{0em}{}[\titlerule]

\begin{document}

% Header
\textbf{\Large Vinay D G} \\Tumakuru, Karnataka – 572106 \quad | \quad +91 91102 44067 \quad | \quad \href{mailto:vinaydg2001@gmail.com}{vinaydg2001@gmail.com} \\\href{https://github.com/LavishPrince}{github.com/LavishPrince} \quad | \quad \href{https://www.linkedin.com/in/vinay-d-g-976207212/}{linkedin.com/in/vinay-d-g-976207212}

% Skills
\section*{Skills}
\textbf{Programming Languages:} Python, Bash, JavaScript, C, C++, SQL, HTML5, CSS3
\textbf{Cloud Platforms:} AWS (Lambda, EC2, S3, CloudFormation, Step Function, Batch, Secrets Manager), Azure (App Service, Blob Storage, Virtual Network)
\textbf{DevOps/Tools:} Docker, Kubernetes, Jenkins, GitHub Actions, Git, Ansible, Nginx, Postman, Terraform, Prometheus, Grafana, Fastlane, Splunk
\textbf{Databases:} PostgreSQL, MySQL, SQLite, Snowflake
\textbf{Frameworks/Libraries:} React, Bootstrap, Flask, Jinja2, REST APIs
\textbf{Methodologies:} Agile, Scrum
\textbf{Operating Systems:} Linux
\textbf{Design:} Figma, Responsive Design

% Profile
\section*{Profile}
A results-driven engineer with 2 years of experience, blending a strong background in Electronics and Communication Engineering with a passion for both robust software development and efficient DevOps practices. Eager to contribute expertise in designing, implementing, and optimizing scalable applications, while also streamlining CI/CD pipelines and ensuring system reliability. Committed to delivering impactful technological solutions through clean code, innovative practices, and a strong understanding of infrastructure.

% Experience
\section*{Experience}
\textbf{DevOps Engineer} \
Travancore Analytics \ \hfill Sep 2023 – Present
\begin{itemize}[leftmargin=0.5in, label=\textbullet]
    \item Designed and implemented robust CI/CD pipelines using Jenkins and GitHub Actions to automate software delivery, reducing deployment time and improving release frequency.
    \item Managed and provisioned cloud infrastructure on AWS and Azure using Infrastructure as Code (IaC) principles with tools like CloudFormation, ensuring scalable and reproducible environments.
    \item Implemented monitoring and logging solutions (e.g., CloudWatch) to ensure system health, proactively identify issues, and optimize application performance.
    \item Collaborated with development teams to integrate security best practices into the SDLC and troubleshoot production issues, enhancing system stability and reliability.
    \item Automated routine operational tasks using scripting (Bash, Python) to improve efficiency and reduce manual intervention.
\end{itemize}


% Projects
\section*{Projects}
	\textbf{Data Integration and Dashboarding Project} – Snowflake, PostgreSQL, AWS QuickSight
\begin{itemize}[leftmargin=0.25in, label=\textbullet]
    \item Developed a robust data pipeline to extract and enrich data from Snowflake, ensuring data quality and consistency.
    \item Integrated processed data into PostgreSQL databases, optimizing for efficient querying and reporting.
    \item Created interactive dashboards in AWS QuickSight, providing key business insights and visualizations from the integrated data.
\end{itemize}


	\textbf{Automated Cloud Infrastructure and CI/CD Platform} – Terraform, Jenkins, Prometheus, Grafana, AWS/Azure
\begin{itemize}[leftmargin=0.25in, label=\textbullet]
    \item Designed and implemented a scalable, automated cloud infrastructure using Terraform across AWS and Azure, ensuring environment consistency.
    \item Developed and optimized Jenkins-based CI/CD pipelines for multiple applications, integrating automated testing and deployment stages.
    \item Established comprehensive monitoring and alerting systems with Prometheus and Grafana, providing real-time insights into application performance and infrastructure health, leading to proactive issue resolution.
    \item Collaborated with development teams to integrate security best practices into the CI/CD process, enhancing overall system resilience and compliance.
\end{itemize}







\textbf{Azure Cloud Solutions} – Azure App Service, Blob Storage, MySQL, Virtual Network
\begin{itemize}[leftmargin=0.25in, label=\textbullet]
    \item Gained extensive experience in architecting and deploying secure, scalable cloud solutions on Azure, utilizing services like Azure App Service, Blob Storage, and MySQL.

    \item Ensured robust backend data isolation within a Virtual Network, enhancing security and compliance.
\end{itemize}

% Education
\section*{Education}
\textbf{B.E. in Electronics and Communication Engineering} \\
PES College of Engineering (PESCE), Mandya \hfill 2019 – 2023 \\
CGPA: 7.51 / 10

\textbf{Pre-University Course (PCMB)} \hfill 2017 – 2019 \\
Mahesh PU College, Tumakuru \\
Percentage: 79.33\%

\textbf{SSLC} \\
Chaithanya Vidya Mandira, Tumakuru \hfill 2016 – 2017 \\
Percentage: 94.56\%

\end{document}

